Trajectories

### 2021-09-15 Rmd/report.Rmd
mode report to Markdown

```{r items_list, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
items %>% 
  pivot_wider(
    id_cols = c("te", "class", "cognate"),
    names_from = "language",
    values_from = c("label", "frequency", "ipa")
  ) %>% 
  clean_names() %>% 
  arrange(te) %>% 
  gt() %>% 
  tab_spanner(label = md("**Catalan**"), columns = contains("_catalan")) %>% 
  tab_spanner(label = md("**Spanish**"), columns = contains("_spanish")) %>% 
  cols_label(
    te = "TE ID",
    class = "Class",
    cognate = "Cognateness",
    label_catalan = "Label",
    label_spanish = "Label",
    ipa_catalan = "Phonology",
    ipa_spanish = "Phonology",
    frequency_catalan = "Frequency",
    frequency_spanish = "Frequency"
  ) %>% 
  fmt_number(columns = starts_with("frequency")) %>% 
  div(style = "height:600px; overflow-x: scroll; overflow-y: scroll", .) %>% 
  as_raw_html()
```

>>>>

```{r items_list, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
items %>% 
  pivot_wider(
    id_cols = c("te", "class", "cognate"),
    names_from = "language",
    values_from = c("label", "frequency", "ipa")
  ) %>% 
  clean_names() %>% 
  arrange(te) %>% 
  gt() %>% 
  tab_spanner(label = md("**Catalan**"), columns = contains("_catalan")) %>% 
  tab_spanner(label = md("**Spanish**"), columns = contains("_spanish")) %>% 
  cols_label(
    te = "TE ID",
    class = "Class",
    cognate = "Cognateness",
    label_catalan = "Label",
    label_spanish = "Label",
    ipa_catalan = "Phonology",
    ipa_spanish = "Phonology",
    frequency_catalan = "Frequency",
    frequency_spanish = "Frequency"
  ) %>% 
  fmt_number(columns = starts_with("frequency")) %>% 
  as_raw_html() %>% 
  div(style = "height:600px; overflow-x: scroll; overflow-y: scroll", .)
```
